---
title: "Logistic Regression Notebook"
output: html_notebook
---
Description:The dataset is about Daily percentage returns for the S&P 500 stock index between 2001 and 2005.
We are going to predict the direction of the market whether it went up or down.
```{r}
require(ISLR)
names(Smarket)
head(Smarket)
```

```{r}
pairs(Smarket,col=Smarket$Direction)
```
There isnt much correlation between the variables
```{r}
summary(Smarket)
```
Lets fit Logistic Regression model using glm
```{r}
glm.fit <- glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume,data= Smarket,family=binomial)
summary(glm.fit)
```
None of the features are significant.
Null deviance - is for the mean,ie. log likelihood if we just use the mean.
Residual deviance - is for the model with all the predictors. 4 units change in deviance with 6 degrees for freedom difference
```{r}
glm.prob <- predict(glm.fit,type="response")
glm.prob[1:5]
```

```{r}
glm.pred <- ifelse(glm.prob > 0.5,"Up","Down")
attach(Smarket)
table(glm.pred,Direction)
```
Mean Classication performance
```{r}
mean(glm.pred==Direction)
```
The data might be overfitting on the training. Lets split the data into train and test and evaluate
```{r}
train <- Year <2005
glm.fit1 <- glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume,data=Smarket,family=binomial,subset = train)
glm.probstest <-predict(glm.fit1,newdata = Smarket[!train,],type="response")
Direction.2005 <- Smarket$Direction[!train]
glm.predtest <-ifelse(glm.probstest>0.5,"Up","Down")
table(glm.predtest,Direction.2005)
mean(glm.predtest==Direction.2005)
```
Still the model seems to be overfitting
```{r}
summary(glm.fit1)
```
Lets use Lag1 and Lag2 variables only to predict as they have the lowes pvalue.
```{r}
#smaller model
glm.fit2 <- glm(Direction~Lag1+Lag2,data=Smarket,family=binomial,subset = train)
glm.probs2 <-predict(glm.fit2,newdata = Smarket[!train,],type="response")

glm.predtest2 <-ifelse(glm.probs2>0.5,"Up","Down")
table(glm.predtest2,Direction.2005)
mean(glm.predtest2==Direction.2005)
```

```{r}
summary(glm.fit2)
```
Still nothing is significant but over model performed better.
