---
title: "R Notebook for Boston Housing Prediction"
output:
  pdf_document: default
  html_document: default
---
```{r}
library(MASS)
library(ISLR)
```


```{r}
names(Boston)
```

This features describe socio-economic condition of Boston.
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.
```{r}
plot(medv~lstat,Boston)
```


```{r}
#fitting the data
fit1 <- lm(medv~lstat,Boston)
summary(fit1)
```

The p-value is less than 0.05 indicating the lstat is significant feature
The negative slope indicates the as the lstat increases the target value medv decreases
```{r}
plot(medv~lstat,Boston)
abline(fit1,col="red")
```

Lets find confidence interval for this fit
```{r}
confint(fit1)
```


```{r}
predict(fit1,data.frame(lstat=c(5,10,15)),interval="confidence")
```

```{r}
fit2 <- lm(medv~lstat+age,Boston)
summary(fit2)
```


```{r}
fitall <- lm(medv~.,Boston)
summary(fitall)
```

The age is no longer significant with all other predicts. Also indus is also not significant
```{r}
par(mfrow=c(2,2))
plot(fitall)
```

The residual plots show non linearity in the data. The third plot shows whether The variance is changing with the mean or not. It seems there is some relationship here.
```{r}
shapiro.test(rstandard(fitall))
```

The Shapiro normality test, the p-value is < 0.05. The residual is not normally distributed. It means we need to improve our model
```{r}
#update the model
fit3 <- update(fitall,~.-age-indus)
summary(fit3)
```

Non Linear terms and Interactions
```{r}
fit4 <- lm(medv~lstat*age,Boston)
summary(fit4)
```
As we can see thought the main effect for age is not significant the interaction between lstat and age is significant
```{r}
#Quadratic
fit5<-lm(medv~lstat+I(lstat^2),Boston);summary(fit5)

```

```{r}
attach(Boston) # the variables can now be used in workspace.
par(mfrow=c(1,1))
plot(medv~lstat)
points(lstat,fitted(fit5),col="red",pch=20) # each value of lstat have fitted values from our quadratic model

```


```{r}
fit6 <- lm(medv~poly(lstat,4))
plot(medv~lstat)
points(lstat,fitted(fit5),col="red",pch=20)
points(lstat,fitted(fit6),col="blue",pch=20)
```

The fit6 model starts to overfit the data.

```{r}

```
